Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2020-01-31 WRITEUP/ms_referee.tex
AP minor comments

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, 
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium 
formation of molecular hydrogen scheme described by \citet{Pallottini17a}. 
{\bf In the simulation, the UV radiation field is assumed to be uniform spatially. 
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription, 
while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as 
part of \ncode{Krome}. % (see \citealt{Bovino16a}). 
We do not assume a clumping factor in the chemistry solver (cf. \citet[][]{Lupi20a}, i.e., $C_\rho$\eq1).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass 
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}$\eq0.07.
Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
of the Milky Way but higher than what is typically observed in the Milky Way}, though the MCCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}

@@

The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures. 
%
{\bf While MCCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MCCs in the local merger-driven ULIRGs}
are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}). {\bf As shown 
by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MCCS of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.

>>>>

The models include a non-equilibrium chemical network (\ncode{Krome}) following e$^{-}$, H$^+$, H$^-$, He, He$^+$, He$^{++}$, H$_2$, 
and H$_2^+$ \citep{Grassi14a,Bovino16a}. Of particular importance here is that the abundances are calculated using an on-the-fly non-equilibrium 
formation of molecular hydrogen scheme described by \citet{Pallottini17a}. 
{\bf In the simulation, the UV radiation field is assumed to be uniform spatially. 
Self-shielding of H$_2$ from photo-dissociation is accounted for using the \citet{Richings14a} prescription, 
while the formation rate on dust grain is computed following \citet{Jura75a}. Effect of photo-dissociation via Lyman-Werner photons is included as 
part of the \ncode{Krome} network. % (see \citealt{Bovino16a}). 
We do not assume a clumping factor in the chemistry solver (i.e., $C_\rho$\eq1, cf. \citealt[][]{Lupi20a}).
In the simulation, \SF follows an H$_2$-based Schmidt-Kennicutt relation.}
% (Section 2.1.1 of \citealt{Pallottini17b})}.

@@

The simulation zooms in on a galaxy named after the flower \flower, whose properties are given in \citet{Pallottini17a} and are briefly summarized in the following. \flower is a Lyman-break galaxy that at $z\simeq 6$ is hosted by a dark matter halo of mass 
{\bf $M_{\rm DM}\simeq$\eq3.5\,$\times$\,10$^{11}$\,\Msun} at the center of a cosmic web knot, and accretes mass from the IGM mainly via three filaments of length $\simeq$\,100\,kpc. \flower has a stellar mass of {\bf $M_\star\simeq$\,2.6\E{10}\,\Msun}, a metallicity of $Z\simeq$\,0.5\,$Z_{\odot}$, a molecular gas mass of $M_{\rm H2}\simeq$\,5\E{7}\,\Msun, and a SFR of 30\,--\,80\,\Msun\,yr\pmOne.
%
The specific SFR of \flower is ${\rm sSFR} \equiv {\rm SFR}/M_{\star} \simeq$~4--40 ~Gyr\pmOne, compatible with the sSFR vs.\ $M_{\star}$ relation observed at high redshift \citep{Jiang16a}. The effective stellar radius of \flower is $\simeq$\,0.5\,kpc and the dark matter virial radius is $r_{\rm 200}\simeq$\,15\,kpc.
{\bf The stellar-to-halo mass ratio of \flower is $M_\star/M_{\rm DM}\,\simeq\,$0.07.
Depending on the work considered, this ratio from abundance matching vary when the halo mass is away from $M_h$\ssim10$^{12}$\,\Msun (see e.g., \citealt{Moster13a, Behroozi13b, Behroozi15a, Moster18a}). The ratio of \flower is higher than e.g., \citet{Katz17a}  and \citet{Ceverino17a} which could be a result of different feedback implementation.
}

@@

While the virial parameter defined as Equation~\ref{eqn:alpha} is typically used in observational studies, as they are designed to probe structures that are composed of mainly molecular gas only, we calculate the virial parameter of MCCs including the influence from the stellar component (i.e., $\alpha_{\rm vir, tot}$ via Equation~\ref{eqn:alpha_tot}) given the high stellar-to-gas mass ratios of some molecular structures identified (see \Fig{stellarRatio16}).
%
The biggest MCC identified at low $n_{\rm cut}$ and with the highest stellar-to-gas mass ratio ($\gtrsim$\,1; \Fig{stellarRatio16}) corresponds to the central main disk of \flower (see top panels of \Fig{MCC} and \Sec{distribution}). The large amount of stellar mass already assembled in \flower explains the low {\em total} virial parameter seen in the middle left panel of \Fig{larsons_single}, where the stellar gravitational potential influences the overall stability. On the other hand, the MCCs in this phase are mostly stable\footnote{We check that the gas-only virial parameter of MCCs is comparable to the {\em total} virial parameter.}, with virial parameter {\bf within the range observed in the molecular structures
of the Milky Way but higher than its average value}, though the MCCs are more massive. {\bf The higher than typical MW value is linked to the higher turbulence of these systems.}

@@

The {\bf total} pressure\footnote{{\bf Non-thermal pressure dominates the total pressure in these high density regions.}} of MCCs identified at the highest $n_{\rm cut}$ ranges from $P/k_B\simeq10^{7-9}$\,{\rm K}\,{\rm cm}$^{-3}$, with a median of $10^{7.6}$\,\,{\rm K}\,{\rm cm}$^{-3}$. Such high pressures are comparable to those observed in local ULIRGs; however, the molecular clouds in these local galaxies are concentrated within their central regions \citep{Downes98a, Sakamoto08a}. In our simulated galaxy, the high pressure MCCs are found throughout the disk. This difference likely stems from the different physical mechanisms giving rise to {\bf the highly turbulent nature} of these molecular structures. 
%
{\bf While MCCs in both local ULIRGs and \flower may form via gravitational instability (see e.g., \citealt{McKee07a}), MCCs in the local merger-driven ULIRGs}
are likely formed by shock compression and cloud-cloud collisions that funnel large amounts of gas from the progenitor galaxies towards the central region (\citealt{Tan00a, Wu18a}; {\bf see \Sec{Qeff} for Toomre-$Q$ analysis on \flower}). {\bf As shown 
by \citet{Kohandel19a} and \citet{Gallerani18a}, the highly turbulent nature seen in the MCCS of \flower result from} extra-planar flows and higher velocity accretion/SN-driven outflows. The presence of extra-planar flows may also be the dominant mode for forming the highly supersonic massive MCCs observed in gas-rich star-forming galaxies at $z$\ssim2. For instance, \citet{Swinbank11a} report ISM pressure of $P/k_B\sim$10$^7$\,K\,\cc and molecular gas mass of $M_{\rm gas}\simeq10^{8-9}$\,\Msun in the star-forming regions of a gas-rich starburst galaxy at \z\eq2.3 based on spatially resolved CO line \obs.
